Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: cleaning text a bit

Having reviewed the modified gravity theories we will consider, we now present
the frameworks upon which we will build our waveform model to confront these
theories against GW observations.
%
We will start by reviewing the theory-agnostic parametrized ringdown
spin-expansion coefficients (ParSpec) expansion in
Sec.~\ref{sec:review_parspec}.
%
Next, in Sec.~\ref{sec:review_pSEOB}, we will review our full
inspiral-(plunge)-merger-ringdown (IMR) BBH waveform model we
use~\cite{Brito:2018rfr,Ghosh:2021mrv} and explain how we include the ParSpec
expansion into it.
%
Finally, in Sec.~\ref{sec:theory_specific_qnm}, we show how we can map
theory-specific QNM calculations in modified gravity theories onto the
theory-agnostic free coefficients in the ParSpec expansion.
%
Ultimately, this provides with an IMR BBH waveform model, with the ringdown
informed with QNM calculations in specific beyond-GR theories.

>>>>

Having reviewed the modified gravity theories we will consider, we now present
the frameworks upon which we will build our waveform model to confront these
theories against GW observations.
%
We will start by reviewing the theory-agnostic parametrized ringdown
spin-expansion coefficients (ParSpec) expansion in Sec.~\ref{sec:review_parspec}.
%
Next, in Sec.~\ref{sec:review_pSEOB}, we will review the
inspiral-(plunge)-merger-ringdown (IMR) BBH waveform
model~\cite{Brito:2018rfr,Ghosh:2021mrv} we will use and explain how we modify
it to include the ParSpec expansion.
%
Finally, in Sec.~\ref{sec:theory_specific_qnm}, we show how we can map
theory-specific QNM calculations in modified gravity theories onto the
theory-agnostic free coefficients in the ParSpec expansion.
%
Ultimately, this provides us with an IMR BBH waveform model, with the ringdown
portion of the model informed by QNM calculations in specific beyond-GR
theories.
